---
title: "Practicing Regular Expressions"
subtitle: "Stat 100 Section"
date: "Week 6"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
#Load tidyverse
library(tidyverse)
```


For the following problems, use `str_view_all()` to identify the pattern with a Regular Expression.

## Problem 1

For this problem we are going to use a subset of the character vector `fruit` that lives in `stringr`.

```{r}
set.seed(4433)
fruit_s <- sample(fruit, 20)
```


a. Highlight the pattern "berry".

```{r}

```

b. Now highlight all the fruits that contain the pattern "berry".  (Don't just highlight the word "berry").

```{r}

```

c. Highlight only fruits that contain "berry" and are one word.

```{r}

```

d. Highlight any repeated characters (e.g. "oo", "ll").

```{r}

```

e. Highlight fruits that start with a vowel.

```{r}

```

f. Highlight fruits that don't start with a vowel.

```{r}

```

g. Highlight the second to last character of fruits that end in a vowel.

```{r}

```

## Problem 2

For this problem, let's continue to use these lyrics about numbers:

```{r}
lyrics <- c("But I would walk 500 miles",
            "2000 0 0 party over oops out of time!", 
            "1 is the loneliest number that you'll ever do",
            "When I'm 64",
            "Where 2 and 2 always makes a 5")
```



a. Locate all words that start with "w" or "W".


```{r}

```

b. Find all the non-numbers.

```{r}

```


c. Locate all the words that are at least five letters long.

```{r}

```

d. Locate all characters that appear after punctuation.

```{r}

```


e. Locate all the places where there are two vowels in a row.


```{r}

```

f. Find words that start with vowels.

Hint: Consider using `\\b` to find the start of the word.

```{r}

```


